---
params:
    source_url: "https://www.quantitativo.com/p/playing-with-the-universe"
title: "Untitled"
format: html
---

# First {.section}

## TODOS

### `libraries`

```{r}
pacman::p_load(
  tidyverse,
  tidyquant, 
  TTR,
  lubridate,
  tictoc
)

### functions
```{r}
#' @title 2-day RSI
calculate_rsi <- function(df) {
  df %>%
    group_by(symbol) %>%
    arrange(date) %>%
    mutate(rsi = RSI(close, n = 2)) %>%
    ungroup()
}

#' @title Normalized ATR
#' @description 14-day Normalized Average True Range (NATR) for each stock.
calculate_natr <- function(df) {
    numeric_cols <- names(df)[sapply(df, is.numeric)]
    # Rename numeric column names to CamelCase
    df %>%
    rename_with(~ tools::toTitleCase(.), .cols = all_of(numeric_cols)) |> 
    arrange(date) %>%
    group_by(symbol) %>%
    mutate(
      atr = select(High, Low, Close) |> ATR(n = 14) , # |> pull('atr'),
      # natr = (atr / close) * 100
    ) 
 
   # as.xts() |> 
    try.xts(error = as.matrix) |>
    TR()


        ATR(n = 14)
  df %>%
    group_by(symbol) %>%
    arrange(date) %>%
    mutate(
      atr = ATR(igh, low, close, n = 14)[, "atr"],
      # natr = (atr / close) * 100
    ) %>%
    ungroup()
}

#' @title entry signals
#' @description Generates entry signals based on the RSI < 5 condition.
generate_entry_signals <- function(df) {
  df %>%
    group_by(symbol) %>%
    arrange(date) %>%
    mutate(entry_signal = lag(rsi < 5)) %>%
    ungroup()
}

#' @title exit signals
#' @description Generates exit signals when the closing price is above the previous day's high.
generate_exit_signals <- function(df) {
  df %>%
    group_by(symbol) %>%
    arrange(date) %>%
    mutate(exit_signal = close > lag(high)) %>%
    ungroup()
}

#' @title simulate trading
#' @description Splitting capital into 10 slots
#' Ranking stocks by NATR
#'   (14-day Normalized Average True Range (NATR))
#' and selecting the top 10
#' Calculating shares to buy, entry and exit costs
#'   (including 1 bps slippage each way)
#' Calculating profit/loss for each trade
simulate_trading <- function(df, initial_capital) {
  capital_per_slot <- initial_capital / 10

  df %>%
    arrange(date) %>%
    group_by(date) %>%
    mutate(
      rank = if_else(entry_signal, rank(-natr), NA_real_),
      trade = if_else(rank <= 10 & !is.na(rank), TRUE, FALSE),
      shares = if_else(trade, floor(capital_per_slot / open), 0),
      entry_cost = if_else(trade, shares * open * 1.0001, 0), # 1 bps slippage
      exit_cost = if_else(lag(trade) & exit_signal, lag(shares) * open * 0.9999, 0), # 1 bps slippage
      pnl = if_else(lag(trade) & exit_signal, exit_cost - lag(entry_cost), 0)
    ) %>%
    ungroup()
}

#' @title Main - run the strategy
run_strategy <- function(df, initial_capital) {
  df %>%
    calculate_rsi() %>%
    calculate_natr() %>%
    generate_entry_signals() %>%
    generate_exit_signals() %>%
    simulate_trading(initial_capital)
}
```

### NASDAQ Data

```{r}

# TODO: Nasdaq-100 constituents?
get_index_symbols <- function(
    # "NASDAQ 100"?
    index = tq_index_options()[1]) {
  tq_index(index) %>%
    pull(symbol)
}
# FIXME: Manual list of Nasdaq-100 constituents (as of a recent date)
get_nasdaq100_symbols <- c(
  "AAPL", "MSFT", "AMZN", "NVDA", "GOOGL", "META", "TSLA", "GOOG", "AVGO", "PEP",
  "COST", "ADBE", "CSCO", "TMUS", "CMCSA", "TXN", "NFLX", "QCOM", "AMD", "INTC",
  "INTU", "AMAT", "PYPL", "BKNG", "HON", "SBUX", "ISRG", "ADP", "GILD", "ADI",
  "MDLZ", "REGN", "VRTX", "FISV", "LRCX", "ATVI", "MU", "CSX", "CHTR", "MAR",
  "MNST", "PANW", "KLAC", "MRVL", "ABNB", "KDP", "KHC", "AEP", "ORLY", "CTAS",
  "FTNT", "ADSK", "NXPI", "PAYX", "EXC", "XEL", "SNPS", "CPRT", "EA", "CDNS",
  "MCHP", "MRNA", "DXCM", "CTSH", "AZN", "PCAR", "WBA", "ROST", "ODFL", "IDXX",
  "VRSK", "FAST", "CSGP", "ANSS", "DLTR", "BIIB", "EBAY", "ZS", "SIRI", "JD",
  "ILMN", "ALGN", "ZM", "TEAM", "WDAY", "LCID", "MTCH", "OKTA", "PDD", "CRWD",
  "ASML", "SGEN", "DDOG", "CEG", "RIVN", "FANG", "TTD", "GEHC"
)

# Function to fetch historical data for a list of symbols
fetch_historical_data <- function(symbols, start_date, end_date) {
  symbols %>%
    tq_get(
      get = "stock.prices",
      from = start_date,
      to = end_date
    ) %>%
    select(date, symbol, open, high, low, close)
}

# Example usage
start_date <- "2020-01-01"
end_date <- Sys.Date() - days(1) # today() - days(1)

# Main function to get Nasdaq-100 data
#  TODO: mirai to parallelise
system.time(
  nasdaq100_data <-
    fetch_historical_data(get_nasdaq100_symbols, start_date, end_date)
)
nasdaq100_data %>% glimpse()

# Summarise data
nasdaq100_summary <- nasdaq100_data %>%
  group_by(symbol) %>%
  summarise(
    start_date = min(date),
    end_date = max(date),
    trading_days = n_distinct(date),
    avg_close = mean(close, na.rm = TRUE)
  )
nasdaq100_summary

```


### Example
```{r}
# Example usage (assuming 'nasdaq100_data' is your input data frame):
# nasdaq100_data should have columns: date, symbol, open, high, low, close

initial_capital <- 1e6L # $1m
tic("run strategy: nasdaq100_data")
results <- run_strategy(
    df = nasdaq100_data, initial_capital)
toc()

# Summarize results
summary <- results %>%
  summarise(
    total_pnl = sum(pnl, na.rm = TRUE),
    total_trades = sum(trade, na.rm = TRUE),
    win_rate = mean(pnl > 0, na.rm = TRUE),
    avg_profit = mean(pnl[pnl > 0], na.rm = TRUE),
    avg_loss = mean(pnl[pnl < 0], na.rm = TRUE)
  )

print(summary)

```

### Notes
implements the 2 basis points total slippage (1 bps for entry, 1 bps for exit) as specified.
Some considerations and potential improvements:

Transaction costs: The script currently only accounts for slippage. You might want to add fixed transaction costs if applicable.
Data quality: Ensure your input data is clean and accounts for stock splits, dividends, etc.
Realistic capital allocation: The script assumes you can always buy shares with the exact amount of capital per slot. In reality, you might not be able to buy fractional shares.
Risk management: You might want to add stop-loss or other risk management features.
